### 2012-08-27 intention motor representation joint action (paper 3)/conf collective intentionality manchester 2012/motor representation and shared intention.tex
before change question

\def \ititle {Motor Representation and Shared Intention}
\def \isubtitle {}
\def \iauthor {
%S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano
}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

{\label{text:second_consideration} A second consideration} in favour of this view is a possible parallel between shared intention and ordinary, individual action.
If you think that events are actions in virtue of being appropriately related to intentions, 
and if you think that shared intention stands to joint action as plain vanilla intention stands to ordinary, individual action,
then it seems reasonable to suppose that for an event to be a joint action is for it to be appropriately related to a shared intention (*cite Pacherie Synthese forthcoming).

\subsection{My view}
But the parallel assumption about ordinary, individual action is not universally accepted. 
In fact, some allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.
For instance, Michael Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.%
\footnote{
For instance, \citet[p.\ 251]{bratman:2000_valuing} % = \citep[p.\ 51]{Bratman:2007bd}
describes an agent called `Creature 2' who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.
}
Others have argued that motor representation and intention are both needed in explaining which events are ordinary, individual actions \citep{pacherie:2000_content,butterfill:2012_intention}.
If any such view is correct, it is impossible to fully explain what it is for an event to be an action by appeal to intention alone.

@@

@@

>>>>

\def \ititle {Motor Representation \\ and Shared Intention}
\def \isubtitle {}
\def \iauthor {
\textit{Collective Intentionality}, Manchester, August 2012}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

{\label{text:second_consideration} A second consideration} in favour of this view is a possible parallel between joint action and ordinary, individual action.
If you think that events are actions in virtue of being appropriately related to intentions, 
and if you think that shared intention stands to joint action as plain vanilla intention stands to ordinary, individual action,
then it seems reasonable to suppose that for an event to be a joint action is for it to be appropriately related to a shared intention (as \citealp{Pacherie:2012fk} suggests).

\subsection{My view}
On the second consideration, 
we take for granted that there is a parallel between joint action and ordinary, individual action.
But is the standard view about the relation between action and intention correct?

Not everyone accepts the standard view.
Some philosophers allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.
For instance, Michael Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally' \citet[p.\ 251]{bratman:2000_valuing}.%
%\footnote{
%For instance, \citet[p.\ 251]{bratman:2000_valuing} % = \citep[p.\ 51]{Bratman:2007bd}
%describes an agent called `Creature 2' who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.
%}

Others reject the standard view without asserting there can be action without intention.
Instead they claim that ingredients other than intention are needed to say which events are actions.
In particular, some claim that motor representation and intention are both needed in explaining which events are ordinary, individual actions \citep{pacherie:2000_content,butterfill:2012_intention}.
If any such view is correct, it is impossible to fully explain what it is for an event to be an action by appeal to intention alone.

@@

\section{Intention and Motor Representation}
So that you can see where this is going, let me briefly explain what stands behind the view that motor representation is needed in addition to intention in saying which events are actions.

@@

[***moved to earlier]
